% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 

  \addtolength{\oddsidemargin}{-.4in}
  \addtolength{\evensidemargin}{-.4in}
  \addtolength{\topmargin}{-.75in}

\usepackage{paralist}
\usepackage{enumitem}
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textheight}{11in} % increase text height to fit on 1-page 


\setlist{nolistsep}


\begin{document} 

\name{\Large{Andrew J. Glaude}\\~~ajgajg1134@csh.rit.edu \\ ~~~github.com/ajgajg1134\\[12pt]}   % the \\[12pt] adds a blank
				        % line after name      

\address{\bf  PERMANENT ADDRESS\\17 Sunset Hill Rd\\Simsbury CT, 06070\\(860) 651-4765}
\address{\bf  PRESENT ADDRESS\\ 2365 Nathaniel Rochester Hall \\  Rochester, NY \\ (860) 690-6033}
                      

                                 
\begin{resume}

\section{1) OBJECTIVE}          
    To obtain a summer job or co-op position that will use and improve my computer science skills.
 
\section{2) EDUCATION}          
	
	    Rochester Institute of Technology, Rochester NY
      \begin{itemize}
          \item Bachelor of Science, Computer Science
	        \item Expected Graduation Year, 2016
	        \item G.P.A. 4.0/4.0
      \end{itemize}
	    Simsbury High School, Simsbury CT
      \begin{itemize}
          \item Graduated 2012
		  \end{itemize}
      \vspace{-.1in}

\section{3) RELEVANT COURSE WORK}
    \begin{itemize}
      \item Data Structures 
      \item Object Oriented Programming
    \end{itemize}

 
\section{4) PERSONAL PROJECTS}
  \vspace{-5pt} 
   \begin{tabbing}%
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions          
   {\bf Settlers of Catan Card App }  \>~~~Personal Project with Team \> ~~~~~~ Work in Progress\\
   \end{tabbing}\vspace{-30pt}
    Developing a Settlers of Catan Board Game app to store and handle cards on Windows Phone 7 and 8
    to interface with board game also in development by a friend. App will use networking to determine
    resources from central game server as well as perform trades with other players.
   \vspace{-5pt}	
   \begin{tabbing}%
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions          
   {\bf Windows Phone 8 App Developer }  \>~~~Computer Science House Major Project \> ~~~~~~ Winter 2012\\
   \end{tabbing}\vspace{-30pt}
    Designed and wrote a flashcards app for Windows Phone 8 in C\# and XAML. This app is located
    on the Windows Phone Marketplace and has nearly 300 users. 
    \vspace{-5pt}
    \begin{tabbing}%
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions          
   {\bf Top-Down XNA 4.0 Game }  \>~~~Computer Science House Game Jam \> ~~~~~~ Winter 2012\\
   \end{tabbing}\vspace{-30pt}
    Created a top down shooter in C\# utilizing the XNA 4.0 libraries. 
    Developed for a Game Jam competition to create a video game from scratch in 24 hours. 
    Also created all design, art, animation and programming done by myself using Gimp 2 and Microsoft Visual Studio 2010.
\section{5) PROFESSIONAL EXPERIENCE}
    \vspace{-5pt}
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf FIRST Robotics Team Captain} \>~~~Simsbury High School, Team \#3464 \> ~~~~~~ 2011-2012\\
   \end{tabbing}\vspace{-30pt}
    Lead a team in the act of creating and competing with a robot as well as general upkeep of the team.
    Duties included facilitating group meetings and teaching new members.
    \vspace{-5pt}
   \begin{tabbing}%
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions          
   {\bf Maintenance Worker }  \>~~~Southington-Cheshire Community YMCA \> ~~~~~~ Summer 2012\\
   \end{tabbing}\vspace{-30pt}
    Duties included general maintenance tasks such as painting, lawn work,
    and cleaning. 
    
\section{6) COMPUTER SKILLS}   
    \vspace{2pt}       
    Proficient in Java, C\#, and Python\\
    Strong knowledge of Windows Operating Systems including Windows XP, 7, and 8\\
    Familiar with Linux(Ubuntu and Arch Linux)
    \vspace{-5pt}
    
\section{7) HONORS AND AWARDS}          
    \vspace{2pt}
    Dean's List: Fall 2012-2013  \\        
    National Honor Society: Simsbury High School  \\        
    1st Place Technology Concepts Connecticut Future Business Leaders of America  2011\\        
    2nd Place Computer Problem Solving Connecticut Future Business Leaders of America 2010\\
    Outstanding Team Leader Connecticut Innovation Academy 2009
    \vspace{-5pt}
 
\section{8) EXTRACURRICULAR ACTIVITIES}        
    \vspace{2pt}
    Computer Science House Member 2012-Present \\  
    Broomball Team - "The Minesweepers" 2012-Present\\     
    Future Business Leaders of America Member 2009 to 2012   
 
\end{resume}
\end{document} 